---
title: "Introduction to resumeMatchR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to resumeMatchR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(project)
```

# Introduction

`resumeMatchR` is a simple R package designed to help users compare resumes and job descriptions using basic text analysis tools.

The package includes functions for:

- counting keywords in text
- finding missing skills in a resume
- calculating a simple similarity score between a resume and a job description

This vignette demonstrates how to use the main functions included in the package.

# Example Dataset

The package includes a sample dataset called `resume_sample_data`.

Load the dataset:

```{r}
data(resume_sample_data)

head(resume_sample_data)
```

The dataset contains:
- candidate names
- target roles
- resume text
- job descriptions

# Counting Keywords

The `count_keywords()` function counts how many times selected keywords appear in a piece of text.

```{r}
count_keywords(
  resume_sample_data$resume_text[1],
  c("Python", "SQL", "Tableau")
)
```

This is useful for checking whether important skills appear in a resume.

# Finding Missing Skills

The `missing_skills()` function identifies skills that appear in the job description but are missing from the resume.

```{r}
missing_skills(
  resume_sample_data$resume_text[1],
  c("Python", "SQL", "Tableau")
)
```

This can help users improve their resumes by identifying missing keywords or skills.

# Calculating Text Similarity

The `text_similarity_simple()` function calculates a simple overlap score between a resume and a job description.

```{r}
text_similarity_simple(
  resume_sample_data$resume_text[1],
  resume_sample_data$job_description[1]
)
```

The similarity score ranges from 0 to 1:
- values closer to 1 indicate higher similarity
- values closer to 0 indicate lower similarity


# Conclusion

`resumeMatchR` provides simple tools for resume and job description analysis. The package demonstrates basic text processing, defensive programming, testing, and package development using the `devtools` ecosystem.
